Class Notes -------

byte consists of 8 slots (bits); each slot can be 0 or 1. 
Signed Integer-> 256 possibilites in a byte, possible combinations = (-127 <-> 128) 

for a # .160117657x10^-18, we'll use:

8bytes
 * 51 bits -> mantissa
 * 13 bits -> exponent
 
 
```{r} 
numToText<-function(num,lang){
      
  
  ex:
    textToNum(zwölf, German)
  how do we get 12? 
  lang==word
      
  WordToNum <- function(lang,word) which(lang==word)-1
  WordToNum(EnglishNumbers,"three")
  }
```

yotta=10^24

10^5 bytes/sec (data used to record a call)
  about 6 hours of each phone conversation for everyone in ze world
  
  ======================
  < > return logicals
  [ ] two inputs: vector or list and an index
  <- declare a variable, assign a value to an object
  grep() 
  grepl()
  sub()
  
EX: {{}}  > gsub('e','*',v)
[1] "b*com*s" "ag*s"  }}
  ><><><><><><><><><><><><><><><><><><><>
  Crossword
  
  grepl("^b.t.$",crossword) = starts with b, any character, t,any character..will give true / false
  use grep to get the number position of the trues
  words(grepl(...),words) to get that word
  
  
  dictionary=c(word='def',
  word='def',
  word='def')
  
  roget(word,dictionary)
  
  dictionary <- c(run="walk fast",sleep="not awake")
  
  roget <- function(word, definitions){
  matched <- grep(word, definitions)
  return(names(definitions)[matched])
  }
  
  ===================================================================
  
  Reserved Words:
    ex: TRUE, FALSE, NULL, NaN, function
  Additional/New Reserved Words:
    ex: if, else, break, for, repeat, next, while, in
    
  myfactorial<-function(n){
  return(prod(1:n))
  }
  
  use a loop to do sum(1:10)
  
```{r}
mysum<-function(n){
  res<-0
  
  for (k in 1:n){
    res<- res+k
    }
  return(res)
  }
```  
}

================OCTOBER 10===================

## Base Conversion

```{r}
baseToNUmeric
```

